Survival Analysis

### 2014-03-29 presentation.Rnw
Reworked introduction
Formatting, worksheet plots timeline

  \begin{frame}{Introduction}
    \begin{center}
      What proportion of the population will\\
      \emph{survive past a given time}?
    \end{center}
  \end{frame}

  % http://rbakker.myweb.uga.edu/pols8501/OxfordOneNotes.pdf
  \begin{frame}{Applications}
    \begin{itemize}
      \item Medical -- How does flu survival differ between countries?
      \item Sociology -- What kind of strikes last more than 3 days?
      \item Engineering -- How long do different F1 tyres last?
      \item Economics -- What affect unemployment duration?
      \item Politics -- How long are civil wars? peaceful times?
      \item Actuarial Science -- How long do people live in cities?
    \end{itemize}
  \end{frame}

>>>>

% http://www.nytimes.com/2011/08/13/health/13meier.html
\begin{frame}{Introduction}
  \begin{center}
    What proportion of the population will\\
    \emph{survive past a given time}?
  \end{center}

  \vspace{0.2in}
  \pause

  \begin{center}
    We are measuring the \emph{time to event}
  \end{center}

  \vspace{0.2in}
  \pause

  \begin{center}
    How do flu durations differ between countries?
  \end{center}
\end{frame}

% http://rbakker.myweb.uga.edu/pols8501/OxfordOneNotes.pdf
\begin{frame}{Applications}
  \begin{itemize}
    % Event History Analysis
    \item Sociology -- What kind of strikes last more than 3 days?
    % Reliability Analysis
    \item Engineering -- How long do different F1 tyres last?
    % Duration Analysis
    \item Economics -- What affect unemployment duration?
    \item Politics -- How long are civil wars? peaceful times?
  \end{itemize}
\end{frame}

\begin{frame}{Data Collection Issues}
<<example-timeline, echo=FALSE, fig=TRUE>>=

@
\end{frame}
